Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-10-06 analysis/paper/paper.Rmd
Updates pkgdown site

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 6.85,
  fig.height = 6.85,
  out.width = "100%",
  dpi = 300
)

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  relative_path = TRUE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 6.85,
  fig.height = 6.85,
  out.width = "100%",
  dpi = 300
)
